---
title: "687 Project"
author: "Ellen Hickman, Wenyi Wang, & Beining Niu"
date: "2026-09-12"
output:
  pdf_document: default
  word_document: default
---
## 1. R Markdown
```{r, include=FALSE}
# Load necessary libraries
library(tidyverse)
library(knitr)
options(scipen = 999)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  tidy = TRUE, 
  tidy.opts = list(comment = FALSE, width.cutoff = 60)
)
```

## 2. Import CVFS data: Labour Outmigration, Agricultural Productivity and Food Security, Nepal, 2015-2017 
```{r}
# A. Load data
github_remittance_url <- paste0(
  "https://github.com/ellenthickman/687Project/raw/",
  "refs/heads/main/36755-0001-Data.rda"
)

temp_env <- new.env()
loaded_names <- load(url(github_remittance_url), envir = temp_env)

loaded_names
remit_w <- temp_env[[loaded_names[1]]]

# B. Select variables
tv_prefixes <- c(
  "A10_", "B11C_", "B12C_", "B13C_",
  "B14C_", "B15C_", "B16B_", "B17_1B_", "B17_2B_",
  "B17_3B_", "B17_4B_", "B17_5B_", "B17_6B_",
  "B17_7B_", "C18_", "C19_", "C20_", "D30B_", "D31B_", "C21_", "REM"
)

remit_w <- remit_w |>
  select(HHID, ETHNICITY,  starts_with(tv_prefixes))

# C. Transform from wide to long
remit_l <- remit_w |>
  pivot_longer(
    cols = matches(
      paste0(
        "^(",
        paste(tv_prefixes, collapse = "|"),
        ")(63|64|65|66|67|68|69|70|71|72)$"
      )
    ),
    names_to = c(".value", "year"),
    names_pattern = "^(.*?)(63|64|65|66|67|68|69|70|71|72)$",
    names_transform = list(year = as.integer)
  )
```
## 3. Clean Data
```{r}
# A. Create a gross farm product
## i. Set variable list
gfp_vars <- c("B11C_", "B12C_", "B13C_",
  "B14C_", "B15C_", "B16B_", "B17_1B_", "B17_2B_",
  "B17_3B_", "B17_4B_", "B17_5B_", "B17_6B_",
  "B17_7B_",  "D30B_", "D31B_")

## ii. Mutate to generate gfp indicator
remit_l <- remit_l |>
  mutate(
    across(
      any_of(gfp_vars),
      ~ as.numeric(as.character(.x))
    ),
    gfp = rowSums(across(any_of(gfp_vars)), na.rm = TRUE)
  )

## iii. Drop extraneous variables 
remit_l <- remit_l |>
  select(-any_of(gfp_vars))

# B. Rename variables
remit_l <- remit_l |>
  rename(
    rem = REM,
    hired_lab = C21_,
    land_owned = A10_,
    hhid = HHID,
    ethnic = ETHNICITY,
    tractor_time = C18_,
    thresher_used = C19_,
    motor_used = C20_
  )

# C. Create farm technology indicator
remit_l <- remit_l |>
  mutate(
    tractor_used = case_when(
      tractor_time == 0 ~ 0,
      tractor_time > 0 & tractor_time <= 6600 ~ 1,
      TRUE ~ NA_real_),
    across(c(thresher_used, motor_used),
           ~ case_when(
             as.character(.x) %in% c("(0) No" , "0")  ~ 0,
             as.character(.x) %in% c("(1) Yes", "1")  ~ 1,
             TRUE ~ NA_real_)),
    farm_tech = tractor_used + thresher_used + motor_used)
```


## 3. Descriptive statistics
Descriptive statistics of the key variables modeling for each household:
$$
gross\ farm\ productivity\ \sim remittances\ + farm\ tech\ +\ \#\ of\ hired\ laborers\ +\ land
$$
### A. Gross farm productivity 
```{r}
remit_l |>
  group_by(year) |>
  summarise(
    Min = min(gfp, na.rm = TRUE),
    Q1 = quantile(gfp, 0.25, na.rm = TRUE),
    Median = median(gfp, na.rm = TRUE),
    Mean = mean(gfp, na.rm = TRUE),
    Q3 = quantile(gfp, 0.75, na.rm = TRUE),
    Max = max(gfp, na.rm = TRUE)
  ) |>
  mutate(across(where(is.numeric), \(x) round(x, 0))) |>
  kable(caption = "Summary of Gross Farm Product by year (Rupees)")
```

### B. Remittances
```{r}
remit_l |>
  group_by(year) |>
  summarise(
    Min = min(rem, na.rm = TRUE),
    Q1 = quantile(rem, 0.25, na.rm = TRUE),
    Median = median(rem, na.rm = TRUE),
    Mean = mean(rem, na.rm = TRUE),
    Q3 = quantile(rem, 0.75, na.rm = TRUE),
    Max = max(rem, na.rm = TRUE)
  ) |>
  mutate(across(where(is.numeric), \(x) round(x, 0))) |>
  kable(caption = "Summary of remittances by year (Rupees)")
```

```{r}
rem_plot <- remit_l |>
  filter(!is.na(rem)) |>
  ggplot(aes(x = rem)) +
  geom_histogram(
    bins = 30, fill = "skyblue", color = "white"
  ) +
  labs(
    title = "Distribution of remittances (orginal scale)",
    subtitle = "years 63-72 combined",
    x = "Remittances (Rupees)",
    y = "Number of observations"
  ) +
  theme_classic()
rem_plot
```

```{r}
rem_plot_log <- remit_l |>
  filter(!is.na(rem), rem >= 0) |>
  ggplot(aes(x = log1p(rem))) +
  geom_histogram(
    bins = 30, fill = "skyblue", color = "white"
  ) +
  labs(
    title = "Distribution of remittances (log-fransformed)",
    subtitle = "Years 63-72 combined",
    x = "ln(1 + remittances)",
    y = "Number of observations"
  ) +
  theme_classic()

rem_plot_log
```


### C. Farm technology --> NOTE: I couldn't find a good indicator of farm technology yet

```{r}
remit_l |>
  group_by(year) |>
  summarise(
    N = sum(!is.na(farm_tech)),
    Missing = sum(is.na(farm_tech)),
    Min = min(farm_tech, na.rm = TRUE),
    Q1 = quantile(farm_tech, 0.25, na.rm = TRUE),
    Median = median(farm_tech, na.rm = TRUE),
    Mean = mean(farm_tech, na.rm = TRUE),
    Q3 = quantile(farm_tech, 0.75, na.rm = TRUE), 
    Max = max(farm_tech, na.rm = TRUE)
    ) |>
  mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  kable(caption = "Summary of farm technology indiactor (0-3) by year")
```

```{r}
farm_tech_all_years_plot <- remit_l |>
  filter(!is.na(farm_tech)) |>
  ggplot(aes(x = factor(farm_tech))) +
  geom_bar(fill = "skyblue") +
  labs(
    title = "Distribution of farm technology indicator (years 63-72 combined)",
    x = "Number of machinery types used",
    y = "Number of observations"
  ) +
  theme_classic()

farm_tech_all_years_plot
```
Note: This plot excludes missing values.

```{r}
#This plot excludes missing values and year 63 (only one valid observation).
farm_tech_by_year_plot <- remit_l |>
  filter(!is.na(farm_tech), year != 63) |>
  ggplot(aes(x = factor(farm_tech, levels = 0:3))) +
  geom_bar(fill = "skyblue") +
  facet_wrap(~ year, ncol = 3) +
  scale_x_discrete(drop = FALSE) +
  labs(
    title = "Distribution of farm technology indicator by year",
    x = "Number of machinery types used",
    y = "Number of household observations") +
  theme_classic()

farm_tech_by_year_plot
```
Note: This plot excludes missing values and data in year 63 (only one observation).

### D. # of Hired laborers
```{r}
remit_l |>
  group_by(year) |>
  summarise(
    Min = min(hired_lab, na.rm = TRUE),
    Q1 = quantile(hired_lab, 0.25, na.rm = TRUE),
    Median = median(hired_lab, na.rm = TRUE),
    Mean = mean(hired_lab, na.rm = TRUE),
    Q3 = quantile(hired_lab, 0.75, na.rm = TRUE),
    Max = max(hired_lab, na.rm = TRUE)
  ) |>
  mutate(across(where(is.numeric), \(x) round(x, 0))) |>
  kable(caption = "Summary of hired laborers by year")
```

```{r}
labor_plot <- remit_l |>
  filter(!is.na(hired_lab)) |>
  ggplot(aes(x = hired_lab)) +
  geom_histogram(
    bins = 30, fill = "skyblue", color = "white"
  ) +
  labs(
    title = "Distribution of hired laborers (years 63-72 combined)",
    x = "Number of hired laborers",
    y = "Number of observations"
  ) +
  theme_classic()

labor_plot
```


### E. Land
```{r}
remit_l |>
  group_by(year) |>
  summarise(
    Min = min(land_owned, na.rm = TRUE),
    Q1 = quantile(land_owned, 0.25, na.rm = TRUE),
    Median = median(land_owned, na.rm = TRUE),
    Mean = mean(land_owned, na.rm = TRUE),
    Q3 = quantile(land_owned, 0.75, na.rm = TRUE),
    Max = max(land_owned, na.rm = TRUE)
  ) |>
  mutate(across(where(is.numeric), \(x) round(x, 2))) |>
  kable(caption = "Summary of land owned by year (Katha)")
```

```{r}
land_plot <- remit_l |>
  filter(!is.na(land_owned)) |>
  ggplot(aes(x = land_owned)) +
  geom_histogram(
    bins = 30, fill = "skyblue", color = "white"
    ) +
  labs(title = "Distribution of land owned (years 63-72 combined)",
       x = "Land owned (Katha)",
       y = "Number of observations") +
  theme_classic()

land_plot
```

### F. Demographics
```{r}
remit_l %>%
  count(ethnic) %>%
  mutate(
    '%' = n / sum(n) * 100
  ) %>%
  kable(caption = "Household ethnicity", digits = 2)
```

### G. Check missing values vs 0 sales
```{r}
raw_data <- temp_env[[loaded_names[1]]]

check_vars <- c(
  "B11C_", "B12C_", "B13C_", "B14C_", "B15C_",
  "B16B_",
  "B17_1B_", "B17_2B_", "B17_3B_", "B17_4B_",
  "B17_5B_", "B17_6B_", "B17_7B_",
  "D30B_", "D31B_"
)

missing_check <- lapply(63:72, function(y) {

  column_names <- paste0(check_vars, y)
  components <- raw_data[, column_names, drop = FALSE]

  stopifnot(all(vapply(components, is.numeric, logical(1))))

  # Number of nonmissing components in each household-year
  n_observed <- rowSums(!is.na(components))

  # Reproduce the original calculation ONLY to diagnose missingness
  original_sum <- rowSums(components, na.rm = TRUE)

  data.frame(
    year = 2000 + y,
    total = nrow(components),
    all_missing = sum(n_observed == 0),
    partially_missing = sum(
      n_observed > 0 & n_observed < length(check_vars)
    ),
    complete = sum(n_observed == length(check_vars)),
    all_missing_but_sum_zero = sum(
      n_observed == 0 & original_sum == 0
    )
  )
})

missing_check <- bind_rows(missing_check)

kable(
  missing_check,
  caption = "Missingness in the original GFP components"
)
```
```





